Optimizing a PoS Tag Set for Dependency Parsing

### 2016-05-06 submission.tex
changes to tag set mapping

\paragraph{Tag Set Mapping}
The tag set modifications are realized by mapping the existing tags to new,
more fine-grained tags "based" on associated morphological features to be
included in specified tags. The procedure maps the relevant existing tags to
new, more fine-grained tags including more relevant morphological features for
the applicable tokens, i.e., tokens that are assigned said tag and feature(s)
in the gold standard data. Hence, we are in actuality altering the gold
standard tags by the addition of more relevant linguistic information,
producing new gold standard annotations of higher quality.

As we want to investigate how we can improve the linguistic quality of a tag
set, we will only consider tag set modifications we deem linguistically
sensible.
%This is done by concatenating the original tag with the
%specified features for all applicable tokens

%contains the set of features in its morphological features.

@@

>>>>

\paragraph{Tag Set Mapping}
The tag set modifications are realized through a mapping procedure that
concatenates the existing tag with one or more specified features for all
applicable tokens, i.e., tokens annotated with said tag and feature(s) in the
gold standard data.
%A given tag set modification involves the specification of
%a tag and the desired features we want to append to the existing,
%coarse-grained tag.

@@

Hence, we are in actuality altering the gold
standard tags by the addition of more relevant linguistic information,
producing new gold standard annotations of higher quality.

As we want to investigate how we can improve the linguistic quality of a tag
set, we will only consider tag set modifications we deem linguistically
sensible.
